---
title: "Data Exploration"
author: "Hieu Nguyen"
date: "2023-03-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploratory_Data_Analysis - Melbourne Housing Prices


```{r}
#install.packages("ggplot2")
library("ggplot2")
```


```{r Question 1: Read file and print summary}
#Question 1: Read file and print summary

house<- read.csv("C:/Users/Hieuhieu/Documents/Intro to R/Input/melbourne_housing_prices.csv")
summary(house)
```


```{r Question 2: Find the missing value in each column }
#Q2. Which variables/vectors have missing data
# count the missing values by column wise
print("Count of missing values by column wise")
sapply(house, function(x) sum(is.na(x)))

```
The data shows us that 3 columns that have missing data: Car, BuildingArea, YearBuilt
- Car variable (int): The household may not have any carspot, so missing value will be assign to 0 

For Landsize and Building Area, these are important factors and the missing value's volumn is moderate compared with the data set, so we can not delete them

- YearBuild: Replace with mean of the column. 
- Building Area: Replace with mean of the column. 


```

```

```{r Missing data}
# Replace NA of Car with 0
house$Car <- replace(house$Car,is.na(house$Car), 0)
summary(house$Car)


# Replace BuildingArea missing value with mean value of that column
house$BuildingArea[is.na(house$BuildingArea)] <- mean(house$BuildingArea,
                                        na.rm = TRUE)
summary(house$BuildingArea)


#Replace Year missing value with mean value of that column
house$YearBuilt[is.na(house$YearBuilt)] <-mean(house$YearBuilt, na.rm = TRUE)
summary(house$YearBuilt)

#Check again to see if we miss anything
sapply(house, function(x) sum(is.na(x)))
```


```{r Question 3 How is the price distributed}
#Question 3 How is the price distribute

#Plot1: Price Histogram
ggplot(house, aes(x = Price)) + 
  stat_bin(bins = 30, fill = "steelblue", color = "white") + 
  labs(x = " Price", y = "count") + 
  ggtitle(" Price Distribution") +
  scale_x_continuous(labels = function(x) paste0("$", format(x, big.mark = ",")))
```
```{r}

```


```{r Scale_x_log10}
#Plot2: Histogram using log10
ggplot(house, aes(x = Price)) + 
  stat_bin(bins = 30, fill = "steelblue", color = "white") + 
  labs(x = "Price", y = "count") + 
  ggtitle(" Price Distribution") +
  scale_x_log10(labels = scales::dollar, 
                breaks = scales::trans_breaks("log10", function(x) 10^x)) 

```


```{r Question 4}
#Q4. Will the number of bedrooms impact the price of the house?
#Plot1
ggplot(house, aes(x = Price, fill = Rooms)) + 
  stat_bin(bins = 30, color = "white") + 
  labs(x = "Prices ($)", y = "Number of House") + 
  scale_x_continuous(labels = scales::dollar_format(scale = 0.001), 
                     limits = c(100000, 3000000)) +
  facet_wrap(~Rooms, scales = "free_x")
             
```

```{r}
```


```{r}
#Plot2:Y-Axis scale for each of these sub-graphs is freed in the second graph.
ggplot(house, aes(x = Price, fill = Rooms)) + 
  stat_bin(binwidth = 100000, color = "white") + 
  labs(x = "Prices ($)", y = "Numbers of Houses") + 
  scale_x_continuous(labels = scales::dollar_format(scale = 0.001), 
                     limits = c(10000, 3000000)) +
  facet_wrap(~Rooms, scales = "free_y")

```

```
```

```{r}
# Question 5:  Create a correlation matrix 
#Print numeric columns
numeric_column_names <- unlist(sapply(house, is.numeric))

# Assign only numeric columns
numeric_cols <- c("Rooms", "Price", "Distance", "Bedroom2", "Car", "Landsize", "BuildingArea")
house_numeric <- house[, numeric_cols]

# Calculate the correlation matrix
corr_matrix <- cor(house_numeric)

# Display the correlation matrix using knitr::kable
knitr::kable(corr_matrix)
```
Correlation coefficients range from -1 to 1, with closer values indicating a stronger linear relationship between the two variables and values closer to 0 indicating a weaker or nonexistent relationship. Based on this correlation matrix, we know that: 


- Rooms and Bedroom2 have a strong positive correlation with Price. The more expensive house will have more rooms and Bedroom2. 

- Variables arrange from highest to smallest influences to Price is: Room, Bedroom2, Car, Building Area, Landsize. 

- The variable Distance has negative coefficient shows that houses are farther from the neighborhood tend to be cheaper. 
